---
title: "Regime-based Implied Stochastic Volatility Model for Crypto Option Pricing"
author: "Saef, Danial; Wang, Yuanrong; Aste, Tomaso"
date: "07/09/2022"
output:
  github_document: 
      number_sections: TRUE
bibliography: iccisvm.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, cache.lazy = FALSE)
```

This library serves as a companion to the publication "Regime-based Implied Stochastic Volatility Model for Crypto Option Pricing". However it can also be used independently for clustering high dimensional datasets and fitting an implied stochastic volatility model.

# Methodology

The increasing adoption of Digital Assets (DAs), such as Bitcoin (BTC), rises the need for accurate option pricing models. Yet, existing methodologies fail to cope with the volatile nature of the emerging DAs. Many models have been proposed to address the unorthodox market dynamics and frequent disruptions in the microstructure caused by the non-stationarity, and peculiar statistics, in DA markets. However, they are either prone to the curse of dimensionality, as additional complexity is required to employ traditional theories, or they overfit historical patterns that may never repeat. 

Instead, we leverage recent advances in market regime (MR) clustering with the Implied Stochastic Volatility Model (ISVM). Time-regime clustering is a temporal clustering method, that clusters the historic evolution of a market into different volatility periods accounting for non-stationarity. ISVM can incorporate investor expectations in each of the sentiment-driven periods by using implied volatility (IV) data. 

In this publication, we applied this integrated time-regime clustering and ISVM method (termed MR-ISVM) to high-frequency data on BTC options at the popular trading platform Deribit. We demonstrate that MR-ISVM contributes to overcome the burden of complex adaption to jumps in higher order characteristics of option pricing models. This allows us to price the market based on the expectations of its participants in an adaptive fashion.

For the exact methodology we refer to the methodology section of this paper, as well as @massara_learning_2019, @procacci_forecasting_2019, @wang_dynamic_2022 for ICC, as well as @ait-sahalia_implied_2021 for the ISVM methodology. Similar implementations can be found in those original works, however not for the MR-ISVM approach.

```{r initialize, message = FALSE, warning = FALSE, results = "hide", echo = FALSE}
#### install and load packages ####
libraries = c("data.table")
lapply(libraries, function(x) if (!(x %in% installed.packages())) {install.packages(x, dependencies = TRUE, repos = "http://cran.us.r-project.org")} )
invisible(lapply(libraries, library, quietly = TRUE, character.only = TRUE))
## ##
#### settings ####
Sys.setenv(LANG = "en") # set environment language to English
Sys.setlocale("LC_TIME", "en_US.UTF-8") # set timestamp language to English
Sys.setlocale("LC_TIME", "English") # set timestamp language to English
## ##
```

# Usage

## Installing

The usage is pretty simple. First, install the package with `devtools`.

```{r install package, message = FALSE, warning = FALSE, echo = TRUE}
library(devtools)
install_github("YalDan/icc.isvm")
library(icc.isvm)
```

## Running the model

Now we can just load a suitable dataset and run the `fit_ICC_ISVM` function. Note that as of now, the bootstrapping estimation of ISVM requires the function `mclapply` from the `parallel` package. This unfortunately won't work on Windows machines. A Windows friendly implementation is however planned in the future, as well as the option to deactivate parallel computing. ICC can also be calculated in parallel setting `parallel_ICC = TRUE`, however this is still experimental and it is recommended to leave it at default. Inside the function `fit_ICC_ISVM` is also a minimalistic example on how to run ICC and ISVM individually.

```{r load data, message = FALSE, warning = FALSE, echo = TRUE}
DT_BTC_deribit_sample <- fread("DT_sample.csv")
ICC_ISVM_list_K2 <- fit_ICC_ISVM(DT_full = DT_BTC_deribit_sample,
                              last_date = as.Date("2022-01-28"),
                              K = 2,
                              gamma = 0.5)
```

If needed, the resulting plots from the model can be saved by using the make_plots function.

```{r plots, message = FALSE, warning = FALSE}
make_plots(ICC_ISVM_list_K2, SAVE_PLOTS = FALSE)
```

# References
